---
title: "Lake Erie Microcystin Risk Assessment -- Without 2017 and 2018"
author: "Song Qian"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial setup
```{r}
source("FrontMatter.R")
load("eriedataClean.RData")
```


## The multi-year BHM model

Using data up to 2016 to develop priors for predicting 2017 and 2018

### Sub-setting data

```{r}
source("BHierM.R") ## model code and input data functions

## Stan model output for all years (except 2017 & 2018)
## Full data
temp1817 <- !is.na(eriedata$part_microcystin) &
  !is.na(eriedata$Chla) & eriedata$Chla> 0 & 
  eriedata$part_microcystin > 0 & 
  eriedata$Year != "2018" & eriedata$Year != "2017"
fit2keep_1817 <- running_fun(Data=eriedata[temp1817,])
save(fit2keep_1817, file="MC_Chla_no18_17.RData")
load("MC_Chla_no18_17.RData")
load("Origin_MC_Chla.RData")
print(fit2keep_1817$fit)
stanout_1817 <- rstan::extract(fit2keep_1817$fit, permuted=T)

## hyper-parameters
beta0_rv_sum <- summary(beta0_rv <- rvsims(stanout_1817$B0))
delta_rv_sum <- summary(delta_rv <- rvsims(stanout_1817$De))
phi_rv_sum   <- summary(phi_rv <- rvsims(stanout_1817$Ph))

## annual values
be0_re_rv_sum<- 
  summary(be0_re_rv <- rvsims(stanout_1817$delB0))
det_re_rv_sum<- 
  summary(det_re_rv <- rvsims(stanout_1817$delD))
phi_re_rv_sum<- 
  summary(phi_re_rv <- rvsims(stanout_1817$delP))
sigma_rv_sum<- 
  summary(sigma_rv <- rvsims(stanout_1817$sigma))

