---
title: "Lake Erie Microcystin Risk Assessment -- Sequential Updating 1"
author: "Song Qian"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Initial setup
```{r}
source("FrontMatter.R")
load("eriedataClean.RData")
source("sequential.R") ## R functions for 
                       ## subsetting data
                       ## prior
                       ## Stan model and input function
```

## Annual Data
```{r}
## Weekly updating
## 2018 data
erie2018 <- erie_sub()
```

## Using Sequential Updating of the Hyper-parameters
1. Summarizing model output to derive prior distribution parameters for the next updating:

Model outputs are used for (1) presenting the estimated MC model and (2) deriving prior distributions for the next model run.

The derived priors are used for model updating. For simplicity, we will assume model parameters are a priori independent of each other (an assumption that requires centering the predictor) and a normal-inverse-gamma conjugate prior.  That is, for each parameter$\theta$ ($=\{\beta_0, \delta, \phi\}$), we use 

$$
\begin{array}{rcl}
\theta & \sim & N(\mu_\theta, \sigma_\theta^2)\\
\mu_\theta | \sigma^2_\theta &\sim& N(\mu^0_{\theta},
\sigma^2_{\theta}/\lambda_\theta)\\ \sigma^2_\theta &\sim&
\Gamma^{-1}(\alpha_{\theta}, \beta_{\theta}) \end{array} 
$$ 

Using the method of moments, we can estimate the prior distribution parameter using the MCMC summaries (mean and variance) of each parameters. That is, the means and variances of the Normal-Inverse-Gamma distribution are: 
$$
\begin{array}{ll}
E(\theta)  = \mu, & Var(\theta) =
\frac{\beta_{\theta}}{(\alpha_{\theta}-1)\lambda_{\theta}}\\
E(\sigma^2_{\theta})  = \frac{\beta_{\theta}}{\alpha_{\theta}-1}, &
Var(\sigma^2_\theta) =
\frac{\beta_{\theta}^2}{(\alpha_{\theta}-1)^2(\alpha_\theta-2)}
\end{array}
$$

Solving for the unknowns:
$$
\begin{align} 
\mu^0_{\theta} = & E(\theta) &
\lambda_{\theta} = E(\sigma^2_{\theta})/Var(\theta)\\ \alpha_{\theta}
= & 2+E^2(\sigma^2_{\theta})/Var(\sigma^2_{\theta}) & \beta_{\theta} =
E(\sigma^2_{\theta})(\alpha_{\theta}-1) \end{align} 
$$

Coding Notes:

- The normal-inverse-gamma conjugate prior is defined for $\sigma^2$, while Stan and R define a normal distribution using $sigma$.  The prior parameters ($\alpha, \beta$) are derived based on the mean and variance of $\sigma^2$.
- Prior parameters were derived using the Stan output after standardization (when used). It is important to separate the fit object and the model coefficient object (the `rv` object). The fit object and its input file should be preserved together.
- The following Stan model is written to monitor $\sigma$.

```{r}
## Function to derive prior distribution parameters from a stan out file.
load("MC_Chla.RData")
print(fit2keep_full$fit)
stanfit_full <- extract(fit2keep_full$fit)

prrs <- rvsims(as.matrix(as.data.frame(stanfit_full))) 

oneYRfit <- function(Year=2018, STD=F, stan_model_compiled,
                     stan_model_compiled_cens,
                     prr=prior(fitrv=prrs, b0="B0", de="De", 
                               ph="Ph",s0="sigma0",
                               sD="sigmaD", sP="sigmaP"), 
                     no1718=F){
  subdata <- erie_sub(Yr=Year)
  fitcoef1 <- fitcoef2 <- list()
  gr <- subdata$gr
  for (i in 1:max(gr)){
	  print(paste(i, "of", max(gr), "Year = ", Year))
##	  if (i >1)
##	    prr <- prior(fitrv=fitcoef1[[i-1]],
##	                 b0="mu0", de="muD", ph="muP")	    
	  tmp <- subdata$gr <= i
    cens <- sum(subdata$part_microcystin[tmp]<=0.01)
    print(paste("No. of censored values:", cens))
	  if (cens==0)
	    input.to.stan <- stan.in(infile=subdata[tmp,], info=T,
	                             prrs=prr, stdz=STD,
	                             n.chains=nchains)
	  else
      input.to.stan <- stan.in_cens(infile=subdata[tmp,], info=T,
	                                  prrs=prr, stdz=STD,
	                                  n.chains=nchains)
	  muxC <- input.to.stan$mux
	  sdxC <- input.to.stan$sdx
	  thetaC <- input.to.stan$data$theta

	  if (cens==0)
	    fit3 <- sampling(stan_model_compiled,
			   data = input.to.stan$data,
			   init = input.to.stan$inits,
			   pars = input.to.stan$para,
			   iter = niters, thin=nthin, 
			   chains=input.to.stan$n.chains)
	  ##control = list(adapt_delta = 0.99, max_treedepth=20))
	  else
	    fit3 <- sampling(stan_model_compiled_cens,
			   data = input.to.stan$data,
			   init = input.to.stan$inits,
			   pars = input.to.stan$para,
			   iter = niters, thin=nthin, 
			   chains=input.to.stan$n.chains)
	  ##control = list(adapt_delta = 0.99, max_treedepth=20))
	  print(fit3)
	  fitcoef1[[i]] <-
   rvsims(as.matrix(as.data.frame(rstan::extract(fit3,
                                                 permute=T))))
	  if (STD){
      fitcoef1[[i]]$delta <- fitcoef1[[i]]$delta/sdxC
      ##fitcoef1[[i]]$beta1 <- fitcoef1[[i]]$beta1/sdxC
      fitcoef1[[i]]$phi <- muxC + fitcoef1[[i]]$phi*sdxC
	  }
  }
  if(no1718)  
    save(fitcoef1, file=paste("No17_18_MC_CHLA_",Year, ".RData", sep=""))
  else save(fitcoef1, file=paste("MC_CHLA_",Year, ".RData", sep=""))
  ## fitting with incremental data
  gr <- subdata$gr
  for (i in 1:max(gr)){
	  print(paste(i, "of", max(gr), "(incremental ", Year, ")"))
	  if (i >1)
	    prr <- prior(fitrv=fitcoef2[[i-1]],
	                 b0="mu0", de="muD", ph="muP")
	  tmp <- subdata$gr == i
    cens <- sum(subdata$part_microcystin[tmp]<=0.01)
    print(paste("No. of censored values:", cens))
	  if (cens==0)
	    input.to.stan <- stan.in(infile=subdata[tmp,], info=T, 
	                           prrs=prr, stdz=STD,
	                           n.chains=nchains)
	  else
	    input.to.stan <- stan.in_cens(infile=subdata[tmp,], info=T, 
	                           prrs=prr, stdz=STD,
	                           n.chains=nchains)
	  muxC <- input.to.stan$mux
	  sdxC <- input.to.stan$sdx
	  thetaC <- input.to.stan$data$theta

	  if(cens==0)
	    fit3_inc<- sampling(stan_model_compiled,
			                  data = input.to.stan$data, 
			                  init=input.to.stan$inits,
			                  pars = input.to.stan$para,
			                  iter=niters, thin=nthin, 
			                  chains=input.to.stan$n.chains)
	  else
	    fit3_inc<- sampling(stan_model_compiled_cens,
			                  data = input.to.stan$data, 
			                  init=input.to.stan$inits,
			                  pars = input.to.stan$para,
			                  iter=niters, thin=nthin, 
			                  chains=input.to.stan$n.chains)
	  print(fit3_inc)
	  fitcoef2[[i]] <- rvsims(
	    as.matrix(as.data.frame(
	      rstan::extract(fit3_inc, permute=T))))
	  if (STD){
	    fitcoef2[[i]]$delta <- fitcoef2[[i]]$delta/sdxC
	    fitcoef2[[i]]$phi <- muxC + fitcoef2[[i]]$phi*sdxC
	  }
  }
  if (no1718) 
    save(fitcoef2, file=paste("No17_18_MC_CHLA_", Year, "_inc.RData",sep=""))
  else
    save(fitcoef2, file=paste("MC_CHLA_",Year, "_inc.RData", sep=""))
  invisible()
}

seq_mod <- stan_model(model_code = stan_model3)
seq_mod_cens <- stan_model(model_code = stan_model3_cens)
  ## 2018
oneYRfit(stan_model_compiled=seq_mod, 
         stan_model_compiled_cens=seq_mod_cens, no1718=F)
  ## 2017
oneYRfit(Year=2017, stan_model_compiled=seq_mod, 
         stan_model_compiled_cens=seq_mod_cens, no1718=F)

## no 17_18
load("MC_Chla_no18_17.RData")
print(fit2keep_1817$fit)
stanout_1817 <- rstan::extract(fit2keep_1817$fit, permuted=T)

prrs <- rvsims(as.matrix(as.data.frame(stanout_1817))) 
oneYRfit(stan_model_compiled=seq_mod, 
         stan_model_compiled_cens=seq_mod_cens, no1718=T)
  ## 2017
oneYRfit(Year=2017, stan_model_compiled=seq_mod,
         stan_model_compiled_cens=seq_mod_cens, no1718=T)


  ## 2016
oneYRfit(Year=2016, stan_model_compiled=seq_mod,
         stan_model_compiled_cens=seq_mod_cens)
  ## 2015
oneYRfit(Year=2015, stan_model_compiled=seq_mod,
         stan_model_compiled_cens=seq_mod_cens)
  ## 2014
oneYRfit(Year=2014, stan_model_compiled=seq_mod,
         stan_model_compiled_cens=seq_mod_cens)
  ## All years
for (yr in 2012:2013) oneYRfit(Year=yr, 
                               stan_model_compiled=seq_mod,
                               stan_model_compiled_cens=seq_mod_cens)

```

