---
title: "Lake Erie Microcystin Risk Assessment -- Other Output"
author: "Song Qian"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial setup
```{r}
source("FrontMatter.R")
load("eriedataClean.RData")
```


```{r}
## No Scum

load("plotting_functions.RData")
load("MC_Chla_noscum.RData")
## fit2keep_noscum <- fit2keep
print(fit2keep_noscum$fit)
stanfit_noscum <- extract(fit2keep_noscum$fit)
## plotting no scum data model ##
#################################

temp <- !is.na(eriedata$part_microcystin) &
  !is.na(eriedata$Chla) & eriedata$Chla> 0 & 
  eriedata$part_microcystin > 0 &
  eriedata$Sample_Depth!=0
yrs <- levels(ordered(eriedata$Year[temp]))

##pdf(file="fitted0_noscum.pdf", width=5, height=4)
tikz(file="fitted0_noscum.tex", width=3, height=2.75, 
     standAlone=F)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plot_full(pltdata=eriedata, sub=temp, stanfit=stanfit_noscum)
dev.off()

pdf(file="fitted_noscum1.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=1, stanfit=stanfit_noscum)
dev.off()

pdf(file="fitted_noscum2.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=2, stanfit=stanfit_noscum)
dev.off()

pdf(paste(plotDIR, "mc_chla10_noscum.pdf", sep="/"),
     height=2.5, width=5.5)#, standAlone=T)
png(file=paste(plotDIR, "mc_chla10yrs.png", sep="/"),
    width=5.5, height=2.5, unit="in", res=350)
par(oma=c(2,2,0,0), mfrow=c(2,5), mar=c(0.25,0.25,0.25,0.25),
    mgp=c(1.25,0.125,0), tck=0.01)
for (i in 1:10){
  plotBYyrs(j=i, Xlab="", Ylab="", Lab1=rep("", 7), 
            Lab2=rep("", 6), stanfit=stanfit_noscum)
  text(x=log(0.5), y=log(125), yrs[i])
}
mtext("Particulate Microcystin", 2, outer=T, line=0.5)
mtext("Chla Concentration", 1, outer=T, line=0.5)
dev.off()

## all medians
tikz(paste(plotDIR, "mc_chlaAll_noscum.tex", sep="/"),
     height=2.5, width=3.5, standAlone=F)
##png(fil=paste(plotDIR, "mc_chlaAll_noscum.png", sep="/"),
##    height=4.5, width=5.5, unit="in", res=350)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
allmedianplt(stanfit=stanfit_noscum)
dev.off()

## plotting no bottom data model ##
###################################
temp <- !is.na(eriedata$part_microcystin) &
  !is.na(eriedata$Chla) & eriedata$Chla> 0 & 
  eriedata$part_microcystin > 0 &
  eriedata$Sample_Depth <= 0.75
yrs <- levels(ordered(eriedata$Year[temp]))

load("MC_Chla_nobottom.RData")
## fit2keep_nobottom <- fit2keep
print(fit2keep_nobottom$fit)
stanfit_nobottom <- extract(fit2keep_nobottom$fit)

##pdf(file="fitted0_nobottom.pdf", width=5, height=4)
tikz(file="fitted0_nobottom.tex", width=3, height=2.75, 
     standAlone=F)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
  plot_full(pltdata=eriedata, sub=temp,
            stanfit=stanfit_nobottom)
dev.off()

for (i in 1:length(yrs)){
  tikz(paste(plotDIR, paste("fitted_nobottom", to2(i), ".tex",
                            sep=""),
             sep="/"),width=5, height=4, standAlone=T)
  par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
  plotBYyrs(j=i, stanfit=stanfit_nobottom)
  dev.off()
}

pdf(file="fitted_nobottom1.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=1, stanfit=stanfit_nobottom)
dev.off()

pdf(file="fitted_nobottom2.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=2, stanfit=stanfit_nobottom)
dev.off()

pdf(paste(plotDIR, "mc_chla10_nobottom.pdf", sep="/"),
    height=2.5, width=5.5)#, standAlone=T)
##png(file=paste(plotDIR, "mc_chla10_nobottom.png", sep="/"),
##    width=5.5, height=2.5, unit="in", res=350)
par(oma=c(2,2,0,0), mfrow=c(2,5), mar=c(0.25,0.25,0.25,0.25),
      mgp=c(1.25,0.125,0), tck=0.01)
for (i in 1:10){
  plotBYyrs(j=i, Xlab="", Ylab="", Lab1=rep("", 7), 
            Lab2=rep("", 6), stanfit=stanfit_nobottom)
  text(x=log(0.5), y=log(125), yrs[i])
}
mtext("Particulate Microcystin", 2, outer=T, line=0.5)
mtext("Chla Concentration", 1, outer=T, line=0.5)
dev.off()

## all medians
tikz(paste(plotDIR, "mc_chlaAll_noscum.tex", sep="/"),
     height=2.5, width=3.5, standAlone=F)
##  png(fil=paste(plotDIR, "mc_chlaAll_noscum.png", sep="/"),
##      height=4.5, width=5.5, unit="in", res=350)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
allmedianplt(stanfit=stanfit_nobottom)
dev.off()

## plotting regular sampling data (0.75) model ##
#################################################
temp <- !is.na(eriedata$part_microcystin) &
  !is.na(eriedata$Chla) & eriedata$Chla> 0 & 
  eriedata$part_microcystin > 0 &
  eriedata$Sample_Depth==0.75
yrs <- levels(ordered(eriedata$Year[temp]))
load("MC_Chla_075.RData")
## fit2keep_075 <- fit2keep
print(fit2keep_075$fit)
stanfit_075 <- extract(fit2keep_075$fit)

##pdf(file="fitted0_075.pdf", width=5, height=4)
tikz(file="fitted0_075.tex", width=3, height=2.75, 
     standAlone=F)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plot_full(pltdata=eriedata, sub=temp, stanfit=stanfit_075)
dev.off()

for (i in 1:length(yrs)){
  tikz(paste(plotDIR, paste("fitted_075", to2(i), ".tex", 
                            sep=""),
             sep="/"),width=5, height=4, standAlone=T)
  par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
  plotBYyrs(j=i, stanfit=stanfit_075)
  dev.off()
}

pdf(file="fitted_0751.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=1, stanfit=stanfit_075)
dev.off()

pdf(file="fitted_0752.pdf", width=5, height=4)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
plotBYyrs(j=2)
dev.off()

pdf(paste(plotDIR, "mc_chla10_075.pdf", sep="/"),
    height=2.5, width=5.5)#, standAlone=T)
##  png(file=paste(plotDIR, "mc_chla10_075.png", sep="/"),
##      width=5.5, height=2.5, unit="in", res=350)
par(oma=c(2,2,0,0), mfrow=c(2,5), mar=c(0.25,0.25,0.25,0.25),
    mgp=c(1.25,0.125,0), tck=0.01)
for (i in 1:10){
  plotBYyrs(j=i, Xlab="", Ylab="", Lab1=rep("", 7), 
            Lab2=rep("", 6), stanfit=stanfit_075)
  text(x=log(0.5), y=log(125), yrs[i])
}
mtext("Particulate Microcystin", 2, outer=T, line=0.5)
mtext("Chla Concentration", 1, outer=T, line=0.5)
dev.off()

clr <- c(rep(1, 9), 4)
lwdth <- c(rep(1,9), 3)
## all medians
tikz(paste(plotDIR, "mc_chlaAll_075.tex", sep="/"),
     height=2.5, width=3.5, standAlone=F)
##png(fil=paste(plotDIR, "mc_chlaAll_noscum.png", sep="/"),
##    height=4.5, width=5.5, unit="in", res=350)
par(mar=c(3,3,1,1), mgp=c(1.25,0.125,0), tck=0.01)
allmedianplt(stanfit=stanfit_075)
dev.off()

